Differential Expression - HBCC - DLPFC - Dx - Sex

### 2021-07-26 individual-cohorts/split_by_analysis/HBCC_DLPFC_DE_Diagnosis.Rmd

# Store contrasts
saveRDS(formula, file = 'CMC_DLPFC_Dx_formula.rds')
ADJ_OBJ = File('CMC_DLPFC_Dx_formula.rds',
               name = 'formula', 
               parentId = CODE$properties$id)
ADJ_OBJ = synStore(ADJ_OBJ, used = ALL_USED_IDs, activityName = activityName,
                   executed = thisFile, activityDescription = activityDescription)
synSetAnnotations(ADJ_OBJ, annotations = all.annotations)
```

>>>>

# Store formula
saveRDS(formula, file = 'CMC_DLPFC_Dx_formula.rds')
ADJ_OBJ = File('CMC_DLPFC_Dx_formula.rds',
               name = 'formula', 
               parentId = CODE$properties$id)
ADJ_OBJ = synStore(ADJ_OBJ, used = ALL_USED_IDs, activityName = activityName,
                   executed = thisFile, activityDescription = activityDescription)
synSetAnnotations(ADJ_OBJ, annotations = all.annotations)
```

### 2021-07-26 individual-cohorts/split_by_analysis/HBCC_DLPFC_DE_DxSex.Rmd
update provenance - all cohorts

# Residuals after normalisation
RESIDUAL.GENE_EXPRESSION = residuals(ADJUSTED.FIT, CQN.GENE_EXPRESSION)
```
`r formula`
### Residual calculation
Calculate weighted residuals and add back "Dx:Sex" to the residuals
```{r varsToAddBack}
# Add variable of interest back to the residuals
varsToAddIn = grep("DxOther:Reported_GenderMale", "DxSCZ:Reported_GenderMale", colnames(ADJUSTED.FIT$design), value = T)
RESIDUAL.GENE_EXPRESSION = RESIDUAL.GENE_EXPRESSION +
  ADJUSTED.FIT$coefficients[,varsToAddIn] %*% t(ADJUSTED.FIT$design[,varsToAddIn])
```

>>>>

# Residuals after normalisation
RESIDUAL.GENE_EXPRESSION = residuals(ADJUSTED.FIT, CQN.GENE_EXPRESSION)
```

### Residual calculation
Calculate weighted residuals and add back "Dx:Sex" to the residuals
```{r varsToAddBack}
# Add variable of interest back to the residuals
varsToAddIn = grep("DxOther:Reported_GenderMale", "DxSCZ:Reported_GenderMale", colnames(ADJUSTED.FIT$design), value = T)
RESIDUAL.GENE_EXPRESSION = RESIDUAL.GENE_EXPRESSION +
  ADJUSTED.FIT$coefficients[,varsToAddIn] %*% t(ADJUSTED.FIT$design[,varsToAddIn])
```
